Automated iterative forecasting for the Portal Project

### 2018-02-02 manuscript/portal_iterative_forecasting_ms.Rmd
Make capitalization of Ernest 2008 consistent

While iterative near-term forecasting is an important next step in the evolution of ecological forecasting, the requirements outlined by Dietze et al (Box 1) are not trivial to implement; few of their recommendations are in widespread use in ecology today. We examined what it would entail to operationalize Dietze et al's recommendations by constructing our own iterative near-term forecasting pipeline for an on-going long-term (~40 year) ecological study that collects high-frequency data on desert rodent abundances [@brown1998; @Ernest2008]. We constructed our forecasting pipeline with the goal of being able to forecast rodent abundances and evaluate our predictions on a monthly basis. In this paper, we discuss our approach for creating this iterative near-term forecasting pipeline, the challenges we encountered, the tools we used, and the lessons we learned so that others can create their own iterative forecasting systems.

>>>>

While iterative near-term forecasting is an important next step in the evolution of ecological forecasting, the requirements outlined by Dietze et al (Box 1) are not trivial to implement; few of their recommendations are in widespread use in ecology today. We examined what it would entail to operationalize Dietze et al's recommendations by constructing our own iterative near-term forecasting pipeline for an on-going long-term (~40 year) ecological study that collects high-frequency data on desert rodent abundances [@brown1998; @ernest2008]. We constructed our forecasting pipeline with the goal of being able to forecast rodent abundances and evaluate our predictions on a monthly basis. In this paper, we discuss our approach for creating this iterative near-term forecasting pipeline, the challenges we encountered, the tools we used, and the lessons we learned so that others can create their own iterative forecasting systems.
